Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Starting a pass over Methodology.

\section{Methodology}
%David TODO: add sentence about the methodology motivation in the overview paragraph. 
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen. Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies. Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

>>>>

\section{Methodology}

Our survey contained two main sections.
In one section, we presented participants with scenarios---something undesirable a wearable device might do---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity of the impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies, following the same methodology as a seminal study in risk perception from Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior risk perception studies, as we describe next.

%Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
